Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-05 exp1/present2013.tex
The factors
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@649 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

>>>>

\begin{frame}{Objective}

To introduce a path to critical practice of evaluations, that makes
use of contemporary statistical techniques, to establish a practice
that can be used to refute assertions on performance.

The focus is didactical, and the experiment we present is a toy
example.

@@

% SECTION

\section{Experiments}

\begin{frame}{Constraints on scope of experiment}

Above all: Easy to understand for newcomers to DoE!

\begin{itemize}
\item Just 2 levels.
\item Handful of illustrative factors.
\item Analysis that illustrates key concepts.
\item Straightforward to program and reproduce.
\item No actual optimization under study.
\end{itemize}

\begin{frame}{Choices to meet these constraints}

  \begin{itemize}
  \item Response variable: Time from DNS lookup finishes to endpoint
    has delivered a full response, measured by \texttt{curl}.
  \item We don't compare different implementions, we compare the
    performance before and after some change.
  \item Query engine: \texttt{4store} where we insert \textsf{sleep}
    statements in the join function on one level and language matching
    function on the other. 
  \end{itemize}

\begin{frame}{Factors and levels}
  \begin{itemize}
  \item [``Implement''] The implementation under evaluation.
  \item [``TripleC''] 1 or 2 MTriples from the DBPedia SPARQL
    Benchmark.
  \item [``Machine''] Software and hardware platform, one smaller
    machine with fast SSD and one larger with slower disks in RAID1.
  \item [``BGPComp''] Two different basic graph patterns with varying
    complexity.
  \item [``Union''] Presence or absence of a \textsf{UNION} pattern.
  \item [``Lang''] Presence or absence of a \textsf{langMatches}
    filter.
  \item [``Range''] Presence or absence of a filter with a larger-than
    operator.
  \item [``Optional''] Presence or absence of an \textsf{OPTIONAL} pattern.
  \end{itemize}
\end{frame}
